Figure 3. Tissue Microbiome Abundances

### 2022-09-30 reports/manuscript/Figure3.Rmd
add library info

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

>>>>

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(vegan)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })
